Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae.

### 2020-10-30 introduction.tex
Minor changes.

This paper is organized as follows. Section II describes the details of the CCSN simulations used in the paper. The algorithm that we employ to extract the time evolution of the PNS surface gravity is discussed in Section III. Section IV shows the performance of our inference method with simulated GW detectors data and presents our main results. Our findings are summarized in section V. Appendix A discusses specific details related to the reconstruction of the g-mode.

>>>>

This paper is organized as follows. Section II provides details of the CCSN simulations used in our work. The algorithm that we employ to extract the time evolution of the PNS surface gravity is discussed in Section III. Section IV shows the performance of our inference method and presents our main results. Finally, our findings are summarized in Section V. Appendix A discusses specific details related to the reconstruction of the g-mode.
